Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-06 ijar-npb-ms.tex
T3 to the right in Fig 4

\begin{figure}
\centering
\begin{tikzpicture}
[type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
 hv path/.style={thick, to path={-| (\tikztotarget)}},
 vh path/.style={thick, to path={|- (\tikztotarget)}}]
%\begin{scope}[scale=0.75]
\node[type1] (T3)   at ( 0  , 0) {T3};
\node[type2] (T2)   at ( 2.8, 0) {T2};
\node[type3] (T1-2) at ( 1.4, 1) {T1};
\node[type3] (T1-3) at ( 1.4,-1) {T1};
\node[type3] (T1-5) at ( 4.2, 1) {T1};
\node[type3] (T1-6) at ( 4.2,-1) {T1};
\coordinate (start) at (-1,0);
\coordinate (end)   at (5.6,0);
\coordinate (bista) at (0.7,0);
\coordinate (biend) at (4.9,0);
\path (start)     edge[thick]   (T3.west)
      (T3.east)   edge[thick]   (bista)
      (bista)     edge[vh path] (T1-2.west)
                  edge[vh path] (T1-3.west)
      (T1-2.east) edge[hv path] (T2.north)
      (T1-3.east) edge[hv path] (T2.south)
      (T2.north)  edge[vh path] (T1-5.west)
      (T2.south)  edge[vh path] (T1-6.west)
      (T1-5.east) edge[hv path] (biend)
      (T1-6.east) edge[hv path] (biend)
      (biend)     edge[thick]   (end);
%\end{scope}
\end{tikzpicture}
\caption{Reliability block diagram for a `bridge' system with three component types.}
\label{fig:bridge-layout}
\end{figure}

>>>>

\begin{figure}
\centering
\begin{tikzpicture}
[type1/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type2/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 type3/.style={rectangle,draw,fill=black!20,very thick,inner sep=0pt,minimum size=8mm},
 cross/.style={cross out,draw=red,very thick,minimum width=7mm, minimum height=5mm},
 hv path/.style={thick, to path={-| (\tikztotarget)}},
 vh path/.style={thick, to path={|- (\tikztotarget)}}]
%\begin{scope}[scale=0.75]
\node[type1] (T3)   at ( 5.6, 0) {T3};
\node[type2] (T2)   at ( 2.8, 0) {T2};
\node[type3] (T1-2) at ( 1.4, 1) {T1};
\node[type3] (T1-3) at ( 1.4,-1) {T1};
\node[type3] (T1-5) at ( 4.2, 1) {T1};
\node[type3] (T1-6) at ( 4.2,-1) {T1};
\coordinate (start) at (0  ,0);
\coordinate (end)   at (6.3,0);
\coordinate (bista) at (0.7,0);
\coordinate (biend) at (4.9,0);
\path (bista)     edge[hv path] (start)
                  edge[vh path] (T1-2.west)
                  edge[vh path] (T1-3.west)
      (T1-2.east) edge[hv path] (T2.north)
      (T1-3.east) edge[hv path] (T2.south)
      (T2.north)  edge[vh path] (T1-5.west)
      (T2.south)  edge[vh path] (T1-6.west)
      (biend)     edge[vh path] (T1-5.east)
                  edge[vh path] (T1-6.east)
                  edge[hv path] (T3.west)
      (T3.east)   edge[hv path] (end);
%\end{scope}
\end{tikzpicture}
\caption{Reliability block diagram for a `bridge' system with three component types.}
\label{fig:bridge-layout}
\end{figure}
